Prefetching SPARQL query cacher

### 2016-05-12 dissertation/cache-proxy.tex
essential debian
mention the test suite
more about the modules

The implementation consists of several modules that have been
published to the Comprehensive Perl Archive Network as Free Software,
and most of which have become a part the Free Software ecosystem. As
such, it builds on the code of hundreds of authors, too long to
enumerate. I shall constrain myself to list the modules that have code
that has been motivated from this study. Modules that have other
primary authors than myself have been started prior to this present
project, but may have substantial contributions from this project. The
Attean framework was started as part of the effort in
Section~\ref{sec:conpush}, but even though it has been developed
further with the requirements that arose from this project and has
contributions from me, the vast majority of the code has been written
my Gregory Todd Williams. The main work in this project has gone into
the module AtteanX::Query::Cache, where I have authored the vast
majority of the code. The relative difference in authorship can be
further examined by checking the linked Github repositories, or by
using git2prov\footnote{see \url{http://git2prov.org/}} to create RDF
data of the commit history. Table~\ref{tab:modules} shows the modules
that have been influenced or written as part of this project.

@@

>>>>

The implementation consists of several modules that have been
published to the Comprehensive Perl Archive Network as Free Software,
and most of which have become a part the Free Software ecosystem. To
install the system on the top of a Debian system with only essential
packages requires 146 Debian packages. Running the test suite requires
even more. As such, it builds on the code of hundreds of authors, too
long to enumerate. I shall constrain myself to list the modules that
have code that has been motivated from this study. Modules that have
other primary authors than myself have been started prior to this
present project, but may have substantial contributions from this
project. The Attean framework was started as part of the effort in
Section~\ref{sec:conpush}, but even though it has been developed
further with the requirements that arose from this project and has
contributions from me, the vast majority of the code has been written
my Gregory Todd Williams. The main work in this project has gone into
the module AtteanX::Query::Cache, where I have authored the vast
majority of the code. The relative difference in authorship can be
further examined by checking the linked Github repositories, or by
using git2prov\footnote{see \url{http://git2prov.org/}} to create RDF
data of the commit history. Table~\ref{tab:modules} shows the modules
that have been influenced or written as part of this project.

@@

To further understand the roles of the different modules, note the following:
LWP::UserAgent::CHICaching is a traits-based \cite{traits} implementation of the
majority of RFC7234. AtteanX::Endpoint is an implementation of the
server side of SPARQL 1.1 Protocol.

\subsection{The Attean framework}

\subsection{SPARQL protocol client}

\subsection{Linked Data Fragment client}
